Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-11-30 src/tex/ms.tex
[showyourwork] overleaf sync

    \section{Application Examples}
    %
    \begin{figure*}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-chandra.pdf}
            \caption{
               \jolideco result \dvd{for}
               %of the \jolideco method applied to 
               \chandra \dvd{observations of} %data of the 
               SNR \textit{1E~0102.2–7219}. The \dvd{bottom} left %large 
               image shows the summed counts from 25 observations. The bottom right image  shows the %result from 
               the \jolideco deconvolution. %process. 
               The flux is given as counts relative to \dvd{obsID}
               %the reference observation with ID=
               1308. The panels \textit{Zoom A}, \textit{Zoom B} and \textit{Zoom C} show a zoomed-in version of three example regions in the SNR, marked with the white rectangles in the large images. The colormap and scale used in the zoom insets is the same as used for the larger images.
            }
            \label{fig:example-chandra}
            \script{example-chandra.py}
        \end{centering}
    \end{figure*}
    %
    \subsection{Deep \chandra Observation}
    \subsubsection{Image Example}
    First we apply \jolideco} to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and combine them into a single long-exposure image using the patch prior learned from JWST data. In total, we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with  the ACIS-S instrument and no grating.

>>>>

    \section{Application Examples}
    %
    \begin{figure*}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/example-chandra.pdf}
            \caption{
               \jolideco result \dvd{for}
               %of the \jolideco method applied to 
               \chandra \dvd{observations of} %data of the 
               SNR \textit{1E~0102.2–7219}. The \dvd{bottom} left %large 
               image shows the summed counts from 25 observations. The bottom right image  shows the %result from 
               the \jolideco deconvolution. %process. 
               The flux is given as counts relative to \dvd{obsID}
               %the reference observation with ID=
               1308. The panels \textit{Zoom A}, \textit{Zoom B} and \textit{Zoom C} show a zoomed-in version of three example regions in the SNR, marked with the white rectangles in the large images. The colormap and scale used in the zoom insets is the same as used for the larger images.
            }
            \label{fig:example-chandra}
            \script{example-chandra.py}
        \end{centering}
    \end{figure*}
    %
    \subsection{Deep \chandra Observation}
    \subsubsection{Image Example}
    First we apply \jolideco to a set of short-exposure \chandra observations of the SNR \textit{1E~0102.2–7219} and combine them into a single long-exposure image using the patch prior learned from JWST data. In total, we chose 25 observations\footnote{Same list of observation IDs as for \url{https://chandra.si.edu/photo/2009/e0102/}} taken with  the ACIS-S instrument and no grating.
